\section{Discussion}
The results support a bounded interpretation of binned spiking reservoirs for affective ERP signal analysis. Under clean static classification, conventional ERP-derived features remain competitive. Under representation-level perturbations, however, the reservoir embedding exhibits a distinct degradation profile, retaining balanced accuracy more strongly than the classical baseline under severe additive noise and dropout. Under raw-signal recomputation, the same embedding remains sensitive to temporal misalignment and channel loss because these perturbations alter the reservoir input trajectory before spike counts are generated.

A reservoir representation is not validated by a single clean accuracy number. It should be characterized by the information it preserves, the transformations it induces, and the conditions under which its dynamics amplify or suppress task-relevant variation. The \BSC{} representation provides temporal traceability because each component corresponds to a post-onset spike-count interval. The recurrent dynamics are fixed, and the downstream readout operates on an extracted representation rather than learning arbitrary temporal filters from the target labels.

Several limitations remain. The dataset is a single affective ERP cohort; the results require external validation before generalization to other EEG paradigms. The study evaluates software-level representations, not neuromorphic hardware energy or latency. The perturbation tests are controlled operating-regime measurements and are not equivalent to full acquisition artifacts. Finally, the present paper isolates the reservoir embedding and does not evaluate graph topology or structure--function coupling.

\section{Conclusion}
This paper evaluated a binned spiking reservoir representation for affective ERP signal analysis under subject-level validation and controlled perturbation tests. The evidence does not support a broad claim that reservoir embeddings dominate classical ERP features for clean static classification. It does support a narrower claim: the reservoir embedding defines a nonlinear temporal measurement operator with a distinct perturbation-response profile. This characterization provides a reproducible basis for studying when event-driven temporal encodings preserve or suppress discriminative structure in biomedical ERP data.
