\balance
\begin{thebibliography}{99}
\bibitem{maass2002real} W. Maass, T. Natschlaeger, and H. Markram, ``Real-time computing without stable states: A new framework for neural computation based on perturbations,'' \emph{Neural Computation}, vol. 14, no. 11, pp. 2531--2560, 2002.
\bibitem{jaeger2004harnessing} H. Jaeger and H. Haas, ``Harnessing nonlinearity: Predicting chaotic systems and saving energy in wireless communication,'' \emph{Science}, vol. 304, no. 5667, pp. 78--80, 2004.
\bibitem{lukosevicius2009reservoir} M. Lukosevicius and H. Jaeger, ``Reservoir computing approaches to recurrent neural network training,'' \emph{Computer Science Review}, vol. 3, no. 3, pp. 127--149, 2009.
\bibitem{roy2019towards} K. Roy, A. Jaiswal, and P. Panda, ``Towards spike-based machine intelligence with neuromorphic computing,'' \emph{Nature}, vol. 575, pp. 607--617, 2019.
\bibitem{lawhern2018eegnet} V. J. Lawhern, A. J. Solon, N. R. Waytowich, S. M. Gordon, C. P. Hung, and B. J. Lance, ``EEGNet: A compact convolutional neural network for EEG-based brain-computer interfaces,'' \emph{Journal of Neural Engineering}, vol. 15, no. 5, 056013, 2018.
\bibitem{craik2019deep} A. Craik, Y. He, and J. L. Contreras-Vidal, ``Deep learning for electroencephalogram classification tasks: A review,'' \emph{Journal of Neural Engineering}, vol. 16, no. 3, 031001, 2019.
\bibitem{makeig2004mining} S. Makeig, M. Westerfield, T.-P. Jung, S. Enghoff, J. Townsend, E. Courchesne, and T. J. Sejnowski, ``Dynamic brain sources of visual evoked responses,'' \emph{Science}, vol. 295, no. 5555, pp. 690--694, 2002.
\bibitem{blankertz2011singletrial} B. Blankertz, S. Lemm, M. Treder, S. Haufe, and K.-R. Mueller, ``Single-trial analysis and classification of ERP components---a tutorial,'' \emph{NeuroImage}, vol. 56, no. 2, pp. 814--825, 2011.
\end{thebibliography}
